\documentclass{mycv}

\name[Eric Seals]{Eric Seals}
\phone{(+1) 785-554-2736}
\email{erjseals@gmail.com}
\github{erjseals}
\linkedin{erjseals}

\begin{document}

\maketitle%

\section{Education}

\subsection{University of Kansas}[Lawrence, KS]
\begin{positions}
    \entry{MS, Computer Engineering, GPA 4.0/4.0}{Aug 2020~--~May 2022}
\end{positions}
\vspace{-\parskip}%
\begin{itemize}[label={}]
    \item Advisor: {Prof.~Heechul Yun}
\end{itemize}

\begin{positions}
    \entry{B. Sc., Computer Engineering, GPA 3.72/4.0}{Aug 2017~--~May 2020}
\end{positions}
\vspace{-\parskip}%

\section{Professional \\ Experience}

\subsection{Garmin International}[Olathe, KS]
\begin{positions}
    \entry{Software Engineer Intern}{Nov 2020~--~Present}
\end{positions}

\begin{itemize}
    \item Wrote software in C++ for the Garmin Overlander and other Automotive GPS devices.
\end{itemize}

\subsection{University of Kansas}[Lawrence, KS]
\begin{positions}
    \entry{Graduate Teaching Assistant}{Aug 2020~--~Present}
\end{positions}

\begin{itemize}
    \item Explained technical topics related to embedded systems and real time applications.
\end{itemize}
 
\vspace{+\parskip}%

\begin{positions}
    \entry{Undergraduate Research Assistant}{Apr 2019~--~May 2020}
\end{positions}

\vspace{-\parskip}%
\begin{itemize}[label={}]
    \item Advisor: {Prof.~Morteza, Hashemi}
\end{itemize}

\begin{itemize}
  \item Designed and built the project Sharp Edges - a research focused project to study the performance gains realized with Mobile Edge Computing.
  \item Built an Android application in Kotlin and a server implementing an Object Detection Model in Java.
\end{itemize}

\vspace{-\parskip}%

\section{Projects}

\subsection{Sharp Edges\normalfont, \href{http://github.com/erjseals/SharpEdgesAndroid}{github.com/SharpEdgesAndroid}}

\begin{itemize}
    \item Demonstrated the substantial performance increase of dedicated servers on-the-edge vs on-device bybuilding a Client/Server system written in Kotlin and Java.
    \item This worked by running the computationally demanding YOLOv3 Object Detection Model on thephone and offloaded to the server.
\end{itemize}

\subsection{Quash “Quite a Shell”\normalfont, \href{http://github.com/erjseals/Quash}{github.com/Quash}}

\begin{itemize}
    \item Programmed a Shell for the UNIX Operating System.
    \item Created features like pipes, main and background thread execution, signal handlers, and job statusreports with C using POSIX libraries.
\end{itemize}
 
\subsection{AudioBud\normalfont, \href{http://github.com/eric-delacruz-prod/AudioBud-Chrome-Extension}{github.com/AudioBud-Chrome-Extension}}

\begin{itemize}
    \item Created an audio visualizer and modulator for both the frequency spectrum and time domain.
    \item Built as a Chrome Extension with JavaScript using the Canvas and Web Audio APIs.
    \item Implemented digital audio filters, user interactivity via an options menu, and the visualizer’s interface.
\end{itemize}

\section{Skills}

\begin{description}
  \item[Programming:] C/C++, Python, Haskell, \LaTeX, Javascript
  \item[Tools:] Vim, Tmux, Git, Linux
  \item[Languages:] English, French
\end{description}

\section{Awards}

\begin{description}
    \item[\normalfont 1st]Prize at Hackathon, HackKU \printdate{2020}
    \item[\normalfont Eta]Kappa Nu, KU's Gamma Iota Chapter \printdate{2019}
    \item[\normalfont Eagle]Scout, Boy Scouts of America \printdate{2013}
\end{description}

\end{document}
